### 2023-05-03 Documentation/UFMG/PFCII/Apendices/ApendiceB.tex
documentation

>>>>

\section{Oscilloscope Impedance}
\label{sec:osc_impedance}

The current is being measured by the Oscilloscope using its internal impedance. 
This oscilloscope model has two impedance options, 1Mohm or 2Mohms. 
Selecting one or other can multiply or divide your current measurement by 2. 
By default we are using the 2Mohm differential input. But it was noticed that using the 1Mohm resistance might reduce the noise. 
A proposal of optimization is to configure the 1Mohm resistance in the \emph{configuration\_tiepie.py} file and evaluate its performance.

### 2023-05-03 Documentation/UFMG/PFCII/LiteratureReview/LiteratureReview.tex
documentation

The electric spray current is a critical variable that has been extensively researched by multiple authors\cite{prunet}\cite{Chen_Pui}\cite{gananCalvo}, resulting in scaling laws that express the relationship between liquid flow rate, conductivity, surface tension, density, and droplet diameter. 
These scaling laws can predict the size and charge of emitted droplets, making them useful tools for electrospraying practitioners. 
Obtaining scaling laws is necessary for characterizing an electrospraying system and gaining a better understanding of the process mechanisms. 
In equation \ref{eq:i_chenpui} we have the current flowing through the charged liquid.

@@

@@

  \begin{figure}[H]
      \center
      \includegraphics[width=3cm]{Figuras/drippingexample.png}
      \label{fig:dripping_camera_example}
      \caption{Dripping}
  \end{figure}

@@

  \begin{figure}[H]
      \center
      \includegraphics[width=3cm]{Figuras/19:03/intermittent_example.png}
      \label{fig:intermittent_example}
      \caption{Intermittent}
  \end{figure}

  \begin{figure}[H]
      \center
      \includegraphics[width=2cm]{Figuras/19:03/intermittent2_example.png}
      \label{fig:intermittent2_example}
      \caption{Intermittent}
  \end{figure}

  \begin{figure}[H]
      \center
      \includegraphics[width=2cm]{Figuras/19:03/microdripping_example.png}
      \label{fig:microdripping_example}
      \caption{Microdripping}
  \end{figure}

@@

  \begin{figure}[H]
      \center
      \includegraphics[width=2cm]{Figuras/april/conjet1.png}
      \label{fig:conjt1}
      \caption{Cone Jet}
  \end{figure}

  \begin{figure}[H]
      \center
      \includegraphics[width=2cm]{Figuras/april/conjet2.png}
      \label{fig:conjt2}
      \caption{Cone Jet}
  \end{figure}

  \begin{figure}[H]
      \center
      \includegraphics[width=2cm]{Figuras/april/conjet3.png}
      \label{fig:conjt3}
      \caption{Cone Jet}
  \end{figure}

@@

>>>>

The electric spray current is a critical variable that has been extensively researched by multiple authors\cite{prunet}\cite{Chen_Pui}\cite{gananCalvo}, resulting in scaling laws that express the relationship between liquid flow rate, conductivity, surface tension, density, and droplet diameter. 
These scaling laws can predict the size and charge of emitted droplets, making them useful tools for electrospraying practitioners. 
Obtaining scaling laws is necessary for characterizing an electrospraying system and gaining a better understanding of the process mechanisms. 
In equation \ref{eq:i_chenpui} we have the current flowing through the charged liquid during a Taylor\cite{taylor} cone jet.

@@

\vspace{2cm}

@@

  \begin{figure}[H]
      \center
      \includegraphics[width=2.9cm]{Figuras/drippingexample.png}
      \label{fig:dripping_camera_example}
      \caption{Dripping}
  \end{figure}

@@

  \begin{figure}[H]
      \center
      \includegraphics[width=2.5cm]{Figuras/19:03/intermittent_example.png}
      \label{fig:intermittent_example}
      \caption{Intermittent 1}
  \end{figure}

  \begin{figure}[H]
      \center
      \includegraphics[width=2cm]{Figuras/19:03/intermittent2_example.png}
      \label{fig:intermittent2_example}
      \caption{Intermittent 2}
  \end{figure}

  \begin{figure}[H]
      \center
      \includegraphics[width=2cm]{Figuras/19:03/microdripping_example.png}
      \label{fig:microdripping_example}
      \caption{Microdripping / Intermittent 3}
  \end{figure}

@@

  \begin{figure}[H]
      \center
      \includegraphics[width=2cm]{Figuras/april/conjet1.png}
      \label{fig:conjt1}
      \caption{Cone Jet 1}
  \end{figure}

  \begin{figure}[H]
      \center
      \includegraphics[width=2cm]{Figuras/april/conjet2.png}
      \label{fig:conjt2}
      \caption{Cone Jet 2}
  \end{figure}

  \begin{figure}[H]
      \center
      \includegraphics[width=2.2cm]{Figuras/april/conjet3.png}
      \label{fig:conjt3}
      \caption{Cone Jet 3}
  \end{figure}

@@

\section{Chapter conclusion}

In this chapter we exhibit some electrospray theory that was important for the development of this project. 
Firstly, with a brief review about the physical concept behind the experiment. 
Then, I introduce how current analysis can be useful for our application citing works already done with this approach.
Finally, I end up the chapter defining what spraying modes classification will be considered and its properties.

### 2023-05-03 Documentation/UFMG/PFCII/Methodology/Methodology.tex
documentation

    The control sequence is the only from our list of sequences that actually uses the feedback classification value. 
    As it is a closed loop control system the controller must be able to stabilize the system in the desired conditions.
    A simple controller algorithm is represented in \ref{alg:simple_controller}, and it was used as a proof of concept.

    \subsection{Simple Controller}

@@

>>>>

    The control sequence is the only from our list of sequences that actually uses the feedback classification value. 
    As it is a closed loop control system the controller must be able to stabilize the system in the desired conditions.
    A simple controller algorithm is represented in \ref{alg:simple_controller}, and it was used as a proof of concept.
    Its results can be seen in results section \ref{sec:controller_results}.

@@

This chapter \ref{chap:Methodology} exhibits how the knowledge from chapter \ref{chap:lit_review} was applied with a control and automation engineering approach in order to achieve our goals. 
Next chapter \ref{chap:Results}, we will discuss the results reached.
